---
title: "P8131-HW8-yz4184"
author: "Yunlin Zhou"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r, echo = T, message = FALSE, results='hide', warning=FALSE}
library(tidyverse)
library(ggplot2)
library(gee)
library(lme4)
library(nlme)
```

```{r, message = FALSE, results='hide', warning=FALSE}
# Import and clean the data
health_df = readxl::read_xlsx("./HW8-HEALTH.xlsx")%>%
  janitor::clean_names()%>%
  drop_na()%>%
  mutate(txt = as.factor(txt),
         health = as.factor(health),
         agegroup = as.factor(agegroup),
         time = as.integer(time))
```

# Part A

First, we plot the count of participants health self-rating counts in different treatment groups.

```{r}
health_random = health_df %>%
  filter(time == 1)

ggplot(data = health_random, aes(x= health, fill = health)) +
  geom_bar() + 
  facet_grid(cols = vars(txt))
```

At the time of randomization, the control group doesn't show significant difference in health self-rating. However, the intervention group shows more poor self-ratings than good  self-ratings.

Then, we would like to use logistic model to test the relationship between randomized group assignment and participants health self-rating.
 
```{r}
glm = glm(health ~ txt,
          family = binomial(link = "logit"),
          data = health_random)

summary(glm)
```

The odds ratio of having good health is expected to be `r exp(glm$coefficients[2])` for intervention group compared to control group.

The p value for the coefficient is 0.486 which is greater than 0.05, which indicates strong evidence for the null hypothesis that there is no correlation between treatment group assignment and health status at the time of randomization.


# Part b

```{r}
health_follow = health_df %>%
  mutate(health = as.numeric(health == "Good"))%>%
  filter(!id %in% names(which(table(health_df$id) == 1)))

resp <- subset(health_follow, time != 1)

resp$baseline <- rep(subset(health_follow, time == 1)$health, as.numeric(table(resp$id)))

resp$nhealth <- as.numeric(resp$health == "Good")

gee = gee(health ~ baseline + txt + time + agegroup,
          family = "binomial",
          corstr = "unstructured",
          id = id,
          scale.fix = FALSE,
          data = resp)

summary(gee)
```

The odds ratio of participants self-rating "good" compared to "poor" is `r exp(gee$coefficients[2])`, at  at the time of randomization, if take average among all measurements and all subjects within the same subgroup. 

The odds ratio of participants self-rating "good" compared to "poor" is `r exp(gee$coefficients[3])`, compare "intervention"  to "control" treatment group, if take average among all measurements and all subjects within the same subgroup. 

The odds ratio of participants self-rating "good" compared to "poor" is `r exp(gee$coefficients[4])`, for the follow-up time after  the time of randomization., if take average among all measurements and all subjects within the same subgroup. 

The odds ratio of participants self-rating "good" compared to "poor" is `r exp(gee$coefficients[5])`, compare 25-34 age group to 15-24 age group, if take average among all measurements and all subjects within the same subgroup. 

The  odds ratio of participants self-rating "good" compared to "poor" is `r exp(gee$coefficients[5])`, compare 35+ age group to 15-24 age group, if take average among all measurements and all subjects within the same subgroup. 


# Part c

```{r}
glmm = glmer(health ~ baseline + txt + time + agegroup + (1 | id),
             family = "binomial",
             data = resp)

summary(glmm)
```

The odds ratio of participants self-rating "good" compared to "poor" is `r exp(2.7813)`, at  at the time of randomization, if take average among all measurements and all subjects within the same subgroup. 

The odds ratio of participants self-rating "good" compared to "poor" is `r exp(3.4231 )`, compare "intervention"  to "control" treatment group, if take average among all measurements and all subjects within the same subgroup. 

The odds ratio of participants self-rating "good" compared to "poor" is `r exp(0.2021)`, for the follow-up time after  the time of randomization., if take average among all measurements and all subjects within the same subgroup. 

The odds ratio of participants self-rating "good" compared to "poor" is `r exp( 2.2587 )`, compare 25-34 age group to 15-24 age group, if take average among all measurements and all subjects within the same subgroup. 

The  odds ratio of participants self-rating "good" compared to "poor" is `r exp(1.9803)`, compare 35+ age group to 15-24 age group, if take average among all measurements and all subjects within the same subgroup.
